Kompilacja przez interpretację:\\ statyczne metaprogramowanie w języku C-=-1

### 2022-02-12 Papers/WUT-Master-Thesis/Grabski-Adam-Magisterska.tex

%--------------------------------------
% Streszczenie po angielsku
%--------------------------------------
\newpage
\abstract \kant[1-3]
\keywords Metaprogramming, Compilers, Interpreters, Programming languages

>>>>

%--------------------------------------
% Streszczenie po angielsku
%--------------------------------------
\newpage
\abstract 
Dynamic metaprogramming, present in many modern, managed programming languages is a powerfull tool, helpful in enhancing programmers productivity and code genericity.
This tool, however, carries with it certain performance penalties, unacceptable in some circumstances.
Nowadays, an increacing number of low level programming languages incorporate static metaprogramming features.
It offers many benefits of dynamic metaprogramming, while transfering its costs from run-time to compile-time.
Currently, static metaprogramming is severley limited, compared to features found in dynamic languages.

This thesis presents a new native programming language: C-=-1, designed with static metaprogramming in mind.
Its core idea is to allow almost any code to be executed at compile-time and to modify the program's structure.
Thus making the C-=-1 as expressive as mannaged languages, without the need for a run-time envoirment.

In order to test C-=-1's capabilities, a basic compiler was implemented in C++, for a small subset of the language.
Despite those limitations, the utlility of proposed metaprogramming features was demonstrated.
C-=-1 makes static analysis easier to perform and the ability to integrate with other languages is improved.
Parts of the compiler were written in C-=-1, thus proving language's utility and boosting it's development.
Implementation of the compiler and conducted tests, indicated new avenues of research into programming languages and compilers.
\keywords Metaprogramming, Compilers, Interpreters, Programming languages

### 2022-02-12 Papers/WUT-Master-Thesis/tex/1-wstep.tex

>>>>

W ramach tej pracy zaprojektowano i zaimplementowano nowy język programowania, jego kompilator oraz bibliotekę standardową.
W rozdziałach \ref{Language_desig} i \ref{implementation} opisano ten proces.
Następnie przeprowadzono badania nad jego użytecznością, przez porównanie z innymi językami, co zostało opisane w rozdziale \ref{comparison}.
